---
title: "Project: Weather-API"
author: "Valentino Mascherini"
date: "26/01/2022"
output:
   bookdown::pdf_document2:
     toc: false
     fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries

library(RPostgres)
library(tidyverse)
library(lubridate)
library(sf)

# tables and figures

cor21 <- read_csv("https://raw.githubusercontent.com/vm17399/weather_api/main/cor_hobos_2021.csv") %>% select(-cov, -meta_id) 

cor22 <- read_csv("https://raw.githubusercontent.com/vm17399/weather_api/main/cor_hobos_2122.csv") %>% select(-cov, -meta_id)

source("https://raw.githubusercontent.com/vm17399/weather_api/main/hobo_api_map_full.R")

source("https://raw.githubusercontent.com/vm17399/weather_api/main/api_hobos_graph.R")

# SQL connection

con <- dbConnect(RPostgres::Postgres(), 
                  "hydenv", host = "localhost",
                  port = 5432, 
                  user = "hydenv", 
                  password = "hydenv")

```

# The variable: air temperature

Air temperature is a good benchmark variable, and for different reasons. First of all, it's quite easy to measure, meaning it doesn't need costly and complex, error prone sensors in order to be recorded. The sensors do not need a particularly time-spending set-up phase, and can be placed almost everywhere, as long as they are out of range of strongly-affecting heat sources. Furthermore, it is the closest measurement we can get in respect to the perceived temperature, making it a great forecast predictor of how the weather will actually affect you.

# Unsuited station data

We can see from the table below (Table \ref{tab:pear}) that the results look at least decent, as every HOBO shows a value higher than 0.5. It has to be noted how last year's data have just a moderately strong correlation with the modeled data, while, on the other hand, 2022's data are very strongly correlated. I would say that the differences are significant, judging by how the most strongly correlated hobo from 2021 cannot break past the 0.8 mark, when for 2022 the weakest is over 0.9. A station from 2021, namely that year's weakest, was placed outside the city of Freiburg and is no wonder why is characterized by such values. This year's weakest is also quite far from this year's best, by around 0.5, but in this case it's not due to a topographical outlier. The plot \ref{fig:points} actually show the correlation of the single HOBOs to the model quite neatly, distinguishing for both terms and thus giving us the general situation at a glance. Here we can we To obtain the said values, Pearson's correlation test was used, instead of a covariance test. My choice is mostly dependent by the fact that a correlation is not affected by a change in scale, a procedure that is absolutely vital in a regionalization context. It's also a really nice tool to investigate a relationship before implementing any kind of model.

```{r pear, echo = FALSE}

knitr::kable(list(cor21, cor22), caption = "Pearson correlation for 2021 and 2022")

```

# Regional differences

Are there regional differences? (max. 250 words)
Given the results of the last task, are there regional differences in correlation between
model and temperature measurements? The needed resolution for ‘regional’ are the different
city districts of Freiburg. Create a map and describe it. Are there differences? Can you find
some good reasons for these differences, like the number of stations or their coverage?
What does that look like if you aggregate the data for each city district?

In order to visualize the regional differences between the model and the actual temperature measurements, I got the mean of the temperature of every HOBO present in a district and tested it through the Pearson correlation against the model data, and plotted it on the Freiburg map (Map \ref{fig:regional}). I first grouped by year and calculated the average district temperature, then I got the average of the correlation per district.
The resolution of the regions are the different city districts, that are filled with different colour corresponding to a certain correlation level. Only the districts with HOBOs actually placed are coloured, thus the majority of the districts furthest to the city center is unfilled. The differences are quite harsh, from 0.9 to less than 0.7. We can see, looking at the areas containing isolated circles, how the 2022 HOBOs have the best correlation, and how the areas with an high ratio of circles over triangles usually have a better ratio, especially than triangles alone. We can conclude that the most correlated districts are the ones who have the most number of new data, making "year" a confounding variable. To have a better understanding of how the districts differ, the map \ref{fig:regional22} shows only the current year's HOBOs. We see that the model correlates best with the devices in the Wiehre district, that has two sensors, a number alike three other areas. To be fair, the districts finding themselves worse off correaltion-wise are those with only one HOBO, so we could say that the more the sensors, the better the correlation. To further support this thesis, I also tried finding the Pearson correlation for each HOBO and then deriving its mean per district, and the distribution was a little different in the districts with more HOBOs, in fact they had a lower correlation than map \ref{fig:regional22}. This means that having more sensors captions an overall temperature average closer to the actual model.

# Database VS Scripts

Both SQL queries and scripts can be exploited in order to achieve the same goal, being initially the display of an overview of the data, then various plots (like Plot \ref{fig:graph}) and maps. However, it has to be accounted for the possibility of automation that scripts entail, due to the possibility of easily storing objects and elements, opposed to the volatility of queries. Furthermore, resources like GitHub and Pastebin making it so that you don't need a specific database connection allow the scripts to be easily designable to function independently.

# Tables, plots and maps

```{sql, connection = con, echo = FALSE}



WITH data_tot AS (
  SELECT * FROM data
  JOIN metadata meta ON data.meta_id=meta.id
  WHERE variable_id=1
),
mean_temp AS (
  SELECT data_tot.id,
  AVG(value) AS t_avg
  FROM data_tot
  GROUP BY data_tot.id
),
day_temp AS (
  SELECT data_tot.id,
  AVG(value) AS t_day
  FROM data_tot
  WHERE date_part('hour', tstamp) >= 6 AND date_part('hour', tstamp) < 18
  GROUP BY data_tot.id
),
night_temp AS (
  SELECT data_tot.id,
  AVG(value) AS t_night
  FROM data_tot
  WHERE date_part('hour', tstamp) < 6 OR date_part('hour', tstamp) >= 18
  GROUP BY data_tot.id
),
t_var AS (
  SELECT tv.id,
  t_max - t_min AS t_t_var
  FROM (
    SELECT  data_tot.id,
    		date_trunc('day', tstamp) AS day,
    MIN(value) AS t_min,
    MAX(value) AS t_max
    FROM data_tot
    GROUP BY data_tot.id, date_trunc('day', tstamp)
  ) tv
),
amount AS (
  SELECT id, count(*) AS "count" FROM data_tot GROUP BY id
)
SELECT  mean_temp.t_avg,
		day_temp.t_day,
		night_temp.t_night,
		t_var.t_t_var,
		amount."count",
		meta.id
FROM metadata meta
JOIN mean_temp ON meta.id=mean_temp.id
JOIN day_temp ON meta.id=day_temp.id
JOIN night_temp ON meta.id=night_temp.id
JOIN amount ON meta.id=amount.id
JOIN t_var ON meta.id=t_var.id
LIMIT 15

```


```{r graph, echo=FALSE, fig.cap="Differences in correlation between HOBOs"}

g0

```

```{r points, echo=FALSE, fig.cap="Differences in correlation between HOBOs"}

g1

```

```{r regional, echo=FALSE, fig.cap="Differences in correlation between city districts 2021 and 2022"}

g5

```

```{r regional22, echo=FALSE, fig.cap="Differences in correlation between city districts 2022"}

g4

```